Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-12 Latex/journal_v1/V4/pr.tex
latex algorithm add

Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
\begin{equation}
\begin{split}
T_{DU}^{s} &= \frac{1}{\mu_d - \alpha_{s}/{M_s^{d}}},\\
T_{CU}^{s} &= \frac{1}{\mu_c - \alpha_{s}/{M_s^{c}}}\\
T_{UPF}^{s} &= \frac{1}{\mu_u - \alpha_{s}/{M_s^{u}}}\\
\end{split}
\end{equation}
Where $M_s^{d}$, $M_s^{c}$ and 
$M_s{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
Moreover, $1/\mu_d$, $1/\mu_c$ and $1/\mu_u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
To convexify \eqref{eq11}, we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}. So, a lower bound for \eqref{eq11} is given that is a concave function.

Suppose UPF, O-CU and O-DU have the same processor 
\begin{lemma}
In problem \eqref{problem}, 
\end{lemma}
\bibliography{ref}
\end{document}

>>>>

Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
\begin{equation}
\begin{split}
T_{DU}^{s} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{CU}^{s} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
T_{UPF}^{s} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\
\end{split}
\end{equation}
Where $M_s^{d}$, $M_s^{c}$ and 
$M_s{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
Moreover, $1/\mu_s^d$, $1/\mu_s^c$ and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
To convexify \eqref{eq11} (for the short packet transmission), we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}. So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{equation}
\begin{split}
\hat{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\hat{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\hat{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}\\
\end{split}
\end{equation}
Consider UPF, O-CU and O-DU have the same processor (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. 
As a result of these assumption, for simplicity, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
Using the above assumption, we have $T_{DU}^{s} = T_{CU}^{s} = T_{UPF}^{s}$ 
\begin{equation}
\begin{split}
T_{process}^{s} &=  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s} \\
T_{process}^{s} &=  T_{RU}^{s} + 3\times T_{DU}^{s}.
\end{split}
\end{equation}
\begin{lemma}
In problem \eqref{problem}, if we change the constraint \eqref{c16} to equality, the optimality of the  
system will not be changed \cite{SystemCostMinimization}
\end{lemma}

\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}
